Baseball

### 2024-02-16 example_projects/baseball/docs/report.qmd

```{.python include="../../../bibat/template/src/data_preparation.py" start-line=44 end-line=57}
```

@@

```{.python include="../../../bibat/template/src/data_preparation.py" start-line=32 end-line=41}
```

>>>>

```{.python include="../../../template/src/data_preparation.py" start-line=44 end-line=57}
```

@@

```{.python include="../../../template/src/data_preparation.py" start-line=32 end-line=41}
```
